\Large{pipeComp, a general framework for the evaluation of computational pipelines, reveals performant single-cell RNA-seq preprocessing tools}

### 2020-02-03 main_figures/clustering.Rmd
changed load_all to pipeComp, fixed calls to internal functions

```{r}
suppressPackageStartupMessages({
  library(ggplot2)
  library(cowplot)
  library(ComplexHeatmap)
  library(matrixStats)
})
source("../misc_functions.R")
suppressMessages(devtools::load_all("../../pipeComp/"))
theme_set(theme_cowplot(font_size = 12))
```

>>>>

```{r}
suppressPackageStartupMessages({
  library(ggplot2)
  library(cowplot)
  library(ComplexHeatmap)
  library
  library(pipeComp)
})
source("../misc_functions.R")
theme_set(theme_cowplot(font_size = 12))
```

### 2020-02-03 main_figures/dimensionality.Rmd
changed load_all to pipeComp, fixed calls to internal functions

```{r}
suppressPackageStartupMessages({
  library(ggplot2)
  library(cowplot)
  library(ComplexHeatmap)
  library(matrixStats)
})
source("../misc_functions.R")
suppressMessages(devtools::load_all("../../pipeComp/"))
source("../../pipeComp/inst/extdata/scrna_alternatives.R")
theme_set(theme_cowplot(font_size = 12))
```

```{r}
o <- readRDS("../../ndims.RDS")
o <- lapply(o, FUN=function(x){
  x$nselected$elbow <- x$nselected$elbow-1
  x
})
o2 <- data.table::rbindlist( lapply(o, FUN=function(x){
  data.frame( method=names(x$nselected), 
              nsel=unlist(x$nselected), 
              time=x$elapsed )
  }), idcol="dataset")
ve <- sapply(o, FUN=function(x) x$varExplained)
row.names(ve) <- 1:nrow(ve)

@@

```{r, fig.width=8, fig.height=4}
res1 <- readRDS("../data/results_dimensionality.rds")
res2 <- readRDS("../data/results_dimensionality2.rds")
sw1 <- res1$dimensionality$clust.avg.silwidth$selected
sw2 <- res2$dimensionality$clust.avg.silwidth$selected
sw2 <- sw2[grep("Local\\.b",row.names(sw2),invert = TRUE),] # redundant
sw <- rbind(sw1,sw2[setdiff(row.names(sw2),row.names(sw1)),])
sw <- sw[grep("=doublet",row.names(sw)),]
n <- sapply(strsplit(row.names(sw),"="),FUN=function(x) rev(x)[1])
w <- grep("seuratvst",row.names(sw))
n[w] <- paste0("sctransform+",n[w])
row.names(sw) <- n
sw2 <- sw[order(grepl("sctransform",row.names(sw))*1000+rowMeans(sw)+apply(sw,1,probs=0.2,FUN=quantile),decreasing=TRUE),order(colMeans(sw),decreasing=TRUE)]
h1 <- Heatmap(sw2, cluster_columns = FALSE, cluster_rows = FALSE, 
        name="silhouette width", col=.silScale(sw2), show_column_names = FALSE,
        column_title = "Subpopulation mean silhouette width",
        bottom_annotation=.ds_anno(colnames(sw2)), heatmap_legend_param = list(direction="horizontal", legend_width=unit(3, "cm")))
p2 <- grid.grabExpr(draw(h1, heatmap_legend_side="bottom"))

>>>>

```{r}
suppressPackageStartupMessages({
  library(ggplot2)
  library(cowplot)
  library(ComplexHeatmap)
  library(matrixStats)
  library(pipeComp)
})
source("../misc_functions.R")
source(system.file("extdata/scrna_alternatives.R", package="pipeComp"))
theme_set(theme_cowplot(font_size = 12))
```

```{r}
o <- readRDS("../data/ndims.RDS")
o <- lapply(o, FUN=function(x){
  x$nselected$elbow <- x$nselected$elbow-1
  x
})
o2 <- data.table::rbindlist( lapply(o, FUN=function(x){
  data.frame( method=names(x$nselected), 
              nsel=unlist(x$nselected), 
              time=x$elapsed )
  }), idcol="dataset")
ve <- sapply(o, FUN=function(x) x$varExplained)
row.names(ve) <- 1:nrow(ve)

@@

```{r, fig.width=8, fig.height=4}
res1 <- readRDS("../data/results_dimensionality.rds")
res2 <- readRDS("../data/results_dimensionality2.rds")
sw1 <- res1$dimensionality$clust.avg.silwidth$selected
sw2 <- res2$dimensionality$clust.avg.silwidth$selected
sw2 <- sw2[grep("Local\\.b",row.names(sw2),invert = TRUE),] # redundant
sw <- rbind(sw1,sw2[setdiff(row.names(sw2),row.names(sw1)),])
sw <- sw[grep("=doublet",row.names(sw)),]
n <- sapply(strsplit(row.names(sw),"="),FUN=function(x) rev(x)[1])
w <- grep("seuratvst",row.names(sw))
n[w] <- paste0("sctransform+",n[w])
row.names(sw) <- n
sw2 <- sw[order(grepl("sctransform",row.names(sw))*1000+rowMeans(sw)+apply(sw,1,probs=0.2,FUN=quantile),decreasing=TRUE),order(colMeans(sw),decreasing=TRUE)]
h1 <- Heatmap(sw2, cluster_columns = FALSE, cluster_rows = FALSE, 
        name="silhouette width", col=pipeComp:::.silScale(sw2), show_column_names = FALSE,
        column_title = "Subpopulation mean silhouette width",
        bottom_annotation=pipeComp:::.ds_anno(colnames(sw2)), heatmap_legend_param = list(direction="horizontal", legend_width=unit(3, "cm")))
p2 <- grid.grabExpr(draw(h1, heatmap_legend_side="bottom"))

### 2020-02-03 main_figures/dr.Rmd
changed load_all to pipeComp, fixed calls to internal functions

```{r}
suppressPackageStartupMessages({
  library(ggplot2)
  library(cowplot)
  library(ComplexHeatmap)
  library(matrixStats)
})
source("../misc_functions.R")
suppressMessages(devtools::load_all("../../pipeComp/"))
```

```{r dimred, fig.width=12, fig.height=6}
res <- readRDS("../data/results_dimred.rds")
x <- res$dimreduction$clust.avg.silwidth
x <- x[grep("norm\\.seurat\\.noscale.*denoise", row.names(x), invert=TRUE),]
x <- x[order(colSums(apply(x,1,prob=c(0.05,0.5),FUN=quantile))+
                         rowMeans(x), decreasing=TRUE),order(colMeans(x), decreasing=TRUE)]
row.names(x) <- gsub("norm\\.","",apply(parsePipNames(row.names(x))[,c("norm","dr")],1,collapse=" + ",FUN=paste))
row.names(x) <- gsub("seuratvst","sctransform",row.names(x))
h1 <- Heatmap(x, cluster_columns = FALSE, cluster_rows = FALSE, 
        name="silhouette width", col=.silScale(x), show_column_names = FALSE,
        column_title = "Subpopulation mean silhouette width", row_names_max_width = unit(9,"cm"),
        bottom_annotation=.ds_anno(colnames(x)), heatmap_legend_param = list(direction="horizontal", legend_width=unit(3, "cm")))
p1 <- grid.grabExpr(draw(h1, heatmap_legend_side="bottom"))

res$clustering <- res$clustering[grep("norm\\.seurat\\.noscale.*denoise", row.names(res$clustering), invert=TRUE),]
h <- scrna_evalPlot_clust(res, what="MI", agg.by=c("norm","dr"), scale=TRUE, anno_legend = FALSE)
h <- h + scrna_evalPlot_clust(res, what="mean_F1", agg.by=c("norm","dr"), scale=TRUE, reorder_rows = h, anno_legend = FALSE) +
  scrna_evalPlot_clust(res, what="min_pr", agg.by=c("norm","dr"), scale=TRUE, reorder_rows = h, anno_legend = FALSE) +
  scrna_evalPlot_clustAtTrueK(res, agg.by=c("norm","dr"), reorder_rows = h, anno_legend = FALSE)
h <- .renameHrows(h, function(x) gsub("; dr=", " + ", gsub("seuratvst", "sctransform", x)))

>>>>

```{r}
suppressPackageStartupMessages({
  library(ggplot2)
  library(cowplot)
  library(ComplexHeatmap)
  library(matrixStats)
  library(pipeComp)
})
source("../misc_functions.R")
```

```{r dimred, fig.width=12, fig.height=6}
res <- readRDS("../data/results_dimred.rds")
x <- res$dimreduction$clust.avg.silwidth
x <- x[grep("norm\\.seurat\\.noscale.*denoise", row.names(x), invert=TRUE),]
x <- x[order(colSums(apply(x,1,prob=c(0.05,0.5),FUN=quantile))+
                         rowMeans(x), decreasing=TRUE),order(colMeans(x), decreasing=TRUE)]
row.names(x) <- gsub("norm\\.","",apply(parsePipNames(row.names(x))[,c("norm","dr")],1,collapse=" + ",FUN=paste))
row.names(x) <- gsub("seuratvst","sctransform",row.names(x))
h1 <- Heatmap(x, cluster_columns = FALSE, cluster_rows = FALSE, 
        name="silhouette width", col=pipeComp:::.silScale(x), show_column_names = FALSE,
        column_title = "Subpopulation mean silhouette width", row_names_max_width = unit(9,"cm"),
        bottom_annotation=pipeComp:::.ds_anno(colnames(x)), heatmap_legend_param = list(direction="horizontal", legend_width=unit(3, "cm")))
p1 <- grid.grabExpr(draw(h1, heatmap_legend_side="bottom"))

res$clustering <- res$clustering[grep("norm\\.seurat\\.noscale.*denoise", row.names(res$clustering), invert=TRUE),]
h <- scrna_evalPlot_clust(res, what="MI", agg.by=c("norm","dr"), scale=TRUE, anno_legend = FALSE)
h <- h + scrna_evalPlot_clust(res, what="mean_F1", agg.by=c("norm","dr"), scale=TRUE, reorder_rows = h, anno_legend = FALSE) +
  scrna_evalPlot_clust(res, what="min_pr", agg.by=c("norm","dr"), scale=TRUE, reorder_rows = h, anno_legend = FALSE) +
  scrna_evalPlot_clustAtTrueK(res, agg.by=c("norm","dr"), reorder_rows = h, anno_legend = FALSE)
h <- pipeComp:::.renameHrows(h, function(x) gsub("; dr=", " + ", gsub("seuratvst", "sctransform", x)))

### 2020-02-03 main_figures/filtering.Rmd
changed load_all to pipeComp, fixed calls to internal functions

```{r}
suppressPackageStartupMessages({
  library(ComplexHeatmap)
  library(circlize)
  library(ggplot2)
  library(ggridges)
  library(cowplot)
  library(SingleCellExperiment)
})
theme_set(theme_cowplot(font_size = 12))
suppressMessages(devtools::load_all("../../pipeComp/"))
source("../misc_functions.R")
data(datasets)
```

>>>>

```{r}
suppressPackageStartupMessages({
  library(ComplexHeatmap)
  library(circlize)
  library(ggplot2)
  library(ggridges)
  library(cowplot)
  library(SingleCellExperiment)
  library(pipeComp)
})
theme_set(theme_cowplot(font_size = 12))
source("../misc_functions.R")
data(datasets)
```

### 2020-02-03 main_figures/imputation.Rmd
changed load_all to pipeComp, fixed calls to internal functions

```{r}
suppressPackageStartupMessages({
  library(ggplot2)
  library(cowplot)
  library(ComplexHeatmap)
  library(matrixStats)
})
source("../misc_functions.R")
suppressMessages(devtools::load_all("../../pipeComp/"))
theme_set(theme_cowplot(font_size = 10))
```

@@

h1 <- Heatmap(dr, cluster_columns = FALSE, col=.silScale(dr), cluster_rows = FALSE, 
        bottom_annotation=dsa,
        show_column_names = FALSE, show_column_dend = FALSE, 
        name="silh.\nwidth", column_title="Mean silhouette width", 
        right_annotation=rowAnnotation( mean=rowMeans(dr, na.rm=TRUE), 
                                        median=rowMedians(dr, na.rm=TRUE), 
                                        min=rowMins(dr, na.rm=TRUE), 
                                        show_legend=FALSE)
        )
p1 <- grid.grabExpr(draw(h1))

@@

myh <- function(k,title=k,...){
  rmLead0 <- sum(abs(ll2[[k]])>1,na.rm=TRUE)==0
  sp <- paste0('sprintf("%.2f", ll2[["',k,'"]][i, j])')
  resmid <- range(ll2s[[k]], na.rm=TRUE)
  resmid <- resmid[1]+(resmid[2]-resmid[1])/2
  cellfn <- eval(parse(text=paste0('function(j, i, x, y, width, height, fill){',
      'lab <- ', ifelse(rmLead0, paste('gsub("^0\\\\.",".",', sp,')'), sp),
      '; grid.text(lab, x, y, gp = gpar(fontsize = 10, 
      col=ifelse(ll2s[["',k,'"]][i,j]>',resmid,',"black","white"))) }')))
  Heatmap(ll2s[[k]], col = viridis::inferno(100), show_column_names = FALSE, bottom_annotation = .ds_anno(colnames(ll2[[k]]), FALSE), cluster_columns=FALSE, cluster_rows = FALSE, show_heatmap_legend = FALSE, column_title=title, cell_fun=cellfn, ...)
}

>>>>

```{r}
suppressPackageStartupMessages({
  library(ggplot2)
  library(cowplot)
  library(ComplexHeatmap)
  library(matrixStats)
  library(pipeComp)
})
source("../misc_functions.R")
theme_set(theme_cowplot(font_size = 10))
```

@@

h1 <- Heatmap(dr, cluster_columns = FALSE, col=pipeComp:::.silScale(dr), cluster_rows = FALSE, 
        bottom_annotation=dsa,
        show_column_names = FALSE, show_column_dend = FALSE, 
        name="silh.\nwidth", column_title="Mean silhouette width", 
        right_annotation=rowAnnotation( mean=rowMeans(dr, na.rm=TRUE), 
                                        median=rowMedians(dr, na.rm=TRUE), 
                                        min=rowMins(dr, na.rm=TRUE), 
                                        show_legend=FALSE)
        )
p1 <- grid.grabExpr(draw(h1))

@@

myh <- function(k,title=k,...){
  rmLead0 <- sum(abs(ll2[[k]])>1,na.rm=TRUE)==0
  sp <- paste0('sprintf("%.2f", ll2[["',k,'"]][i, j])')
  resmid <- range(ll2s[[k]], na.rm=TRUE)
  resmid <- resmid[1]+(resmid[2]-resmid[1])/2
  cellfn <- eval(parse(text=paste0('function(j, i, x, y, width, height, fill){',
      'lab <- ', ifelse(rmLead0, paste('gsub("^0\\\\.",".",', sp,')'), sp),
      '; grid.text(lab, x, y, gp = gpar(fontsize = 10, 
      col=ifelse(ll2s[["',k,'"]][i,j]>',resmid,',"black","white"))) }')))
  Heatmap(ll2s[[k]], col = viridis::inferno(100), show_column_names = FALSE, bottom_annotation = pipeComp:::.ds_anno(colnames(ll2[[k]]), FALSE), cluster_columns=FALSE, cluster_rows = FALSE, show_heatmap_legend = FALSE, column_title=title, cell_fun=cellfn, ...)
}

### 2020-02-03 main_figures/normalization.Rmd
changed load_all to pipeComp, fixed calls to internal functions

```{r}
suppressPackageStartupMessages({
  library(ggplot2)
  library(cowplot)
  library(ComplexHeatmap)
  library(matrixStats)
})
suppressMessages(devtools::load_all("../../pipeComp/"))
source("../misc_functions.R")
theme_set(theme_cowplot(font_size = 11))
renameNorm <- function(x){
  .renameHrows(x, f=function(x){
    x <- gsub("^norm\\.", "", x)
    x <- gsub("seuratvst","sctransform",x)
    x <- gsub(".noscale", " (no scaling)", x)
  })
}
```

>>>>

```{r}
suppressPackageStartupMessages({
  library(ggplot2)
  library(cowplot)
  library(ComplexHeatmap)
  library(matrixStats)
  library(pipeComp)
})
source("../misc_functions.R")
theme_set(theme_cowplot(font_size = 11))
renameNorm <- function(x){
  .renameHrows(x, f=function(x){
    x <- gsub("^norm\\.", "", x)
    x <- gsub("seuratvst","sctransform",x)
    x <- gsub(".noscale", " (no scaling)", x)
  })
}
```

### 2020-02-03 main_figures/selection.Rmd
changed load_all to pipeComp, fixed calls to internal functions

```{r}
suppressPackageStartupMessages({
  library(SingleCellExperiment)
  library(ggplot2)
  library(cowplot)
  library(ComplexHeatmap)
  library(matrixStats)
})
source("../misc_functions.R")
suppressMessages(devtools::load_all("../../pipeComp/"))
data(datasets)
theme_set(theme_cowplot(font_size = 12))
```

>>>>

```{r}
suppressPackageStartupMessages({
  library(SingleCellExperiment)
  library(ggplot2)
  library(cowplot)
  library(ComplexHeatmap)
  library(matrixStats)
  library(pipeComp)
})
source("../misc_functions.R")
data(datasets)
theme_set(theme_cowplot(font_size = 12))
```

### 2020-02-03 supplementary_figures/supp1_dataset_description.Rmd
changed load_all to pipeComp, fixed calls to internal functions

```{r}
suppressPackageStartupMessages({
  library(ggplot2)
  library(cowplot)
  library(SingleCellExperiment)
  library(scater)
  library(reshape2)
  library(pheatmap)
})
suppressMessages(devtools::load_all("../../pipComp/"))
theme_set(theme_cowplot(font_size = 12))
# we load the datasets
lf <- list.files("../datasets/", full.names=TRUE)
names(lf) <- gsub(".SCE.rds", "", basename(lf), fixed=TRUE)
lf <- lf[grep("simMix", lf, invert=TRUE)]
SCEs <- lapply(lf, readRDS)
```

>>>>

```{r}
suppressPackageStartupMessages({
  library(ggplot2)
  library(cowplot)
  library(SingleCellExperiment)
  library(scater)
  library(reshape2)
  library(pheatmap)
  library(pipeComp)
})
source("../misc_functions.R")
theme_set(theme_cowplot(font_size = 12))
# we load the datasets
lf <- list.files("../datasets/", full.names=TRUE)
names(lf) <- gsub(".SCE.rds", "", basename(lf), fixed=TRUE)
lf <- lf[grep("simMix", lf, invert=TRUE)]
SCEs <- lapply(lf, readRDS)
```

### 2020-02-03 supplementary_figures/supp2_filtering.Rmd
changed load_all to pipeComp, fixed calls to internal functions

```{r, include=FALSE}
suppressPackageStartupMessages({
  library(ggplot2)
  library(cowplot)
  library(SingleCellExperiment)
  library(reshape2)
  library(ComplexHeatmap)
  library(knitr)
  library(circlize)
})
suppressMessages(devtools::load_all("../../pipeComp/"))
source("../misc_functions.R")
load("../../pipComp/data/datasets.RData")
```

@@

```{r}
res <- readRDS("../data/selection_old.rds")
res <- res[grep("deviance|seurat.variance.standardized",res$sel),]
res$filt <- as.factor(res$filt)
levels(res$filt) <- c("coding only", "no mitochondrial", "no ribosomal", "all")
res2 <- res[which(abs(res$nbClusters-datasets[res$dataset,"subpopulations"])<=1),]
ll <- lapply(split(res2, res2$norm), FUN=function(x){
  m2 <- cast2(x, formula=filt~dataset, fun.aggregate=median, value.var="ARI")
})
chm(ll, scale="column", scaleTitle="z-score", sameScale=TRUE, value_format="%.2f", row_sortFn=function(x,...){ median(x,...) }, cluster_columns=FALSE)
```

>>>>

```{r, include=FALSE}
suppressPackageStartupMessages({
  library(ggplot2)
  library(cowplot)
  library(SingleCellExperiment)
  library(reshape2)
  library(ComplexHeatmap)
  library(knitr)
  library(circlize)
  library(pipeComp)
})
source("../misc_functions.R")
```

@@

```{r}
res <- readRDS("../data/selection_old.rds")
res <- res[grep("deviance|seurat.variance.standardized",res$sel),]
res$filt <- as.factor(res$filt)
levels(res$filt) <- c("coding only", "no mitochondrial", "no ribosomal", "all")
res2 <- res[which(abs(res$nbClusters-truek[res$dataset])<=1),]
ll <- lapply(split(res2, res2$norm), FUN=function(x){
  m2 <- cast2(x, formula=filt~dataset, fun.aggregate=median, value.var="ARI")
})
chm(ll, scale="column", scaleTitle="z-score", sameScale=TRUE, value_format="%.2f", row_sortFn=function(x,...){ median(x,...) }, cluster_columns=FALSE)
```

### 2020-02-03 supplementary_figures/supp3_normalization.Rmd
changed load_all to pipeComp, fixed calls to internal functions

```{r}
suppressPackageStartupMessages({
  library(ggplot2)
  library(cowplot)
  library(ComplexHeatmap)
  library(reshape2)
  library(dplyr)
  library(viridis)
})
suppressMessages(devtools::load_all("../../pipComp/"))
data(datasets)
theme_set(theme_cowplot(font_size = 11))
source("../misc_functions.R")
```

@@

```{r norm_nbClusters, fig.width=8, fig.height=8.5}
res <- readRDS("../data/norm2_endSummary.rds")
res2 <- res[which(res$filt=="deffilter" & res$norm %in% c("norm.scran", "norm.scran.noscale", "norm.seurat", "norm.seuratvst", "norm.stableGsum")),]
res2$diff.nbClusters <- res2$nbClusters-datasets[res2$dataset,"subpopulations"]
res3 <- aggregate(res2[,"diff.nbClusters"], by=res2[,c("dataset","dims","resolution","norm")], FUN=mean)
colnames(res3)[5] <- "nb"
res3$norm <- gsub("norm.","",res3$norm, fixed=T)
# ggplot(res3, aes(factor(dims), factor(resolution), fill=nb)) + stat_bin2d() + 
#   scale_fill_viridis() + ylab("Resolution") + xlab("Number of dimensions") +
#   theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
#   coord_flip() + facet_grid(dataset~norm)

>>>>

```{r}
suppressPackageStartupMessages({
  library(ggplot2)
  library(cowplot)
  library(ComplexHeatmap)
  library(reshape2)
  library(dplyr)
  library(viridis)
  library(pipeComp)
})
suppressMessages(devtools::load_all("../../pipComp/"))
theme_set(theme_cowplot(font_size = 11))
source("../misc_functions.R")
```

@@

```{r norm_nbClusters, fig.width=8, fig.height=8.5}
res <- readRDS("../data/norm2_endSummary.rds")
res2 <- res[which(res$filt=="deffilter" & res$norm %in% c("norm.scran", "norm.scran.noscale", "norm.seurat", "norm.seuratvst", "norm.stableGsum")),]
res2$diff.nbClusters <- res2$nbClusters-truek[res2$dataset]
res3 <- aggregate(res2[,"diff.nbClusters"], by=res2[,c("dataset","dims","resolution","norm")], FUN=mean)
colnames(res3)[5] <- "nb"
res3$norm <- gsub("norm.","",res3$norm, fixed=T)
# ggplot(res3, aes(factor(dims), factor(resolution), fill=nb)) + stat_bin2d() + 
#   scale_fill_viridis() + ylab("Resolution") + xlab("Number of dimensions") +
#   theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
#   coord_flip() + facet_grid(dataset~norm)

### 2020-02-03 supplementary_figures/supp4_selection.Rmd
changed load_all to pipeComp, fixed calls to internal functions

suppressPackageStartupMessages({
  library(ggplot2)
  library(cowplot)
  library(ComplexHeatmap)
})
suppressMessages(devtools::load_all("../../pipComp/"))
data(datasets)
source("../misc_functions.R")
```

>>>>

suppressPackageStartupMessages({
  library(ggplot2)
  library(cowplot)
  library(ComplexHeatmap)
  library(pipeComp)
})
source("../misc_functions.R")
```

### 2020-02-03 supplementary_figures/supp5_dr.Rmd
changed load_all to pipeComp, fixed calls to internal functions

```{r}
suppressPackageStartupMessages({
  library(ggplot2)
  library(cowplot)
  library(ComplexHeatmap)
  library(reshape2)
  library(dplyr)
})
theme_set(theme_cowplot(font_size = 13))
suppressMessages(devtools::load_all("../../pipComp/"))
data(datasets)
source("../misc_functions.R")
```

@@

```{r, fig.width=8, fig.height=8.5}
library(viridis)
res <- readRDS("../data/clust_endSummary.rds")
res2 <- res[which(res$clust=="clust.seurat" & res$k==20 & res$dims>2),]
res2 <- res2[which(res2$dr=="seurat.pca" & res2$dataset!="Kumar"),]
res2$diff.nbClusters <- res2$nbClusters-datasets[res2$dataset,"subpopulations"]
res3 <- aggregate(res2[,"diff.nbClusters"], by=res2[,c("dataset","dims","resolution")], FUN=mean)
colnames(res3)[4] <- "nb"
ll <- lapply(split(res3, res3$dataset), FUN=function(x){
  ggplot(x, aes(factor(dims), factor(resolution), fill=nb)) + stat_bin2d() + 
    scale_fill_viridis() + ylab("Resolution") + xlab("Number of dimensions") +
    theme(axis.text.x = element_text(angle = 90, hjust = 1))
})
for(i in names(ll)) ll[[i]] <- ll[[i]] + ggtitle(i)
plot_grid(plotlist = ll, nrow=3)
```

>>>>

```{r}
suppressPackageStartupMessages({
  library(ggplot2)
  library(cowplot)
  library(ComplexHeatmap)
  library(reshape2)
  library(dplyr)
  library(pipeComp)
  library(viridis)
})
theme_set(theme_cowplot(font_size = 13))
source("../misc_functions.R")
```

@@

```{r, fig.width=8, fig.height=8.5}
res <- readRDS("../data/clust_endSummary.rds")
res2 <- res[which(res$clust=="clust.seurat" & res$k==20 & res$dims>2),]
res2 <- res2[which(res2$dr=="seurat.pca" & res2$dataset!="Kumar"),]
res2$diff.nbClusters <- res2$nbClusters-truek[res2$dataset]
res3 <- aggregate(res2[,"diff.nbClusters"], by=res2[,c("dataset","dims","resolution")], FUN=mean)
colnames(res3)[4] <- "nb"
ll <- lapply(split(res3, res3$dataset), FUN=function(x){
  ggplot(x, aes(factor(dims), factor(resolution), fill=nb)) + stat_bin2d() + 
    scale_fill_viridis() + ylab("Resolution") + xlab("Number of dimensions") +
    theme(axis.text.x = element_text(angle = 90, hjust = 1))
})
for(i in names(ll)) ll[[i]] <- ll[[i]] + ggtitle(i)
plot_grid(plotlist = ll, nrow=3)
```

### 2020-02-03 supplementary_figures/supp6_clust.Rmd
changed load_all to pipeComp, fixed calls to internal functions

suppressPackageStartupMessages({
  library(ggplot2)
  library(cowplot)
  library(ComplexHeatmap)
  library(reshape2)
  library(dplyr)
  library(patchwork)
})
theme_set(theme_cowplot(font_size = 12))
devtools::load_all("../../pipeComp/")
source("../misc_functions.R")
```

>>>>

suppressPackageStartupMessages({
  library(ggplot2)
  library(cowplot)
  library(ComplexHeatmap)
  library(reshape2)
  library(dplyr)
  library(patchwork)
  library(pipeComp)
})
theme_set(theme_cowplot(font_size = 12))
source("../misc_functions.R")
```

### 2020-02-03 supplementary_figures/supp_figures.Rmd
updated supplementary figures
added DR-related supplementaries
updated supp
changed load_all to pipeComp, fixed calls to internal functions

---
title: "Supplementary Figures"
author: "Pierre-Luc Germain"
date: "`r format(Sys.time(), '%d %B, %Y')`"
geometry: margin=1.5cm
output:
  pdf_document:
    keep_tex: true
    toc: true
    fig_width: 8
    fig_height: 6
    citation_package: natbib
bibliography: ../bmc_article.bib
---

@@

>>>>

---
title: \Large{pipeComp, a general framework for the evaluation of computational pipelines, reveals performant single-cell RNA-seq preprocessing tools}
subtitle: \vspace{0.5cm}\LARGE{Supplementary Figures}\vspace{0.5cm}
author:
- "Pierre-Luc Germain"
- "Anthony Sonrel"
- "Mark D. Robinson"
date: "`r format(Sys.time(), '%d %B, %Y')`"
geometry: margin=1.5cm
output:
  pdf_document:
    keep_tex: true
    toc: true
    fig_width: 8
    fig_height: 6
    citation_package: natbib
bibliography: ../bmc_article.bib
---

\renewcommand{\thepage}{S\arabic{page}}

@@

```{r child='supp2_filtering.Rmd'}
```

```{r child='supp3_normalization.Rmd'}
```

```{r child='supp4_selection.Rmd'}
```

```{r child='supp5_dr.Rmd'}
```

```{r child='supp6_clust.Rmd'}
```
